Sparse Matrix Vector Multiplication with Multiple vectors and Multiple Matrices on the MIC Architecture

### 2013-10-18 ieee_paper.tex
matrix layout

In term of memory layout, we adopt a format similar to the ELLPACK
format to store the matrix since the number of nonzeros per row is
constant throughout the matrix. The matrix is given in two arrays. The
first one is the classical {\tt col\_id} array that describes the
sparsity structure of the matrix. Each row of {\tt col\_id} consists
of $n_z$ entries that label the column index of each nonzero in
$A$. The other array is the {\tt data} array that gives the values of
the nonzeros in the four matrices. The values of the matrices are
interleaved by group of four so that the value $A^l_{col\_id[k]}$ of
the $k$th nonzero of the $l$th matrix is at index $\floor{\frac{k-1}{4}}*4*n_m + (l-1)*4+(k-1)\%4$.
(In other words, the first 4 entries are from $A^{1}$ and the next 4 are from $A^2$.) The vectors {\tt x} are
interleaved so that {\tt x}$^l_i$ and {\tt x}$^{l+1}_i$ are
consecutive in memory. The vector {\tt y} is similarly interleaved,
grouped in sets of 16, which correspond to four derivatives applied to
four functions, at a single point.

>>>>

In term of memory layout, we adopt a format similar to the ELLPACK
format to store the matrix since the number of nonzeros per row is
constant throughout the matrix. The matrix is given in two arrays. The
first one is the classical {\tt col\_id} array that describes the
sparsity structure of the matrix. Each row of {\tt col\_id} consists
of $n_z$ entries that label the column index of each nonzero in
$A$. The other array is the {\tt data} array that gives the values of
the nonzeros in the four matrices. The values of the matrices are
interleaved by group of four so that the value $A^l_{col\_id[k]}$ of
the $k$th nonzero of the $l$th matrix is at index $\floor{\frac{k-1}{4}}*4*n_m + (l-1)*4+(k-1)\%4$.\todo{check that formula}
(In other words, the first 4 entries are from $A^{1}$ and the next 4 are from $A^2$.) The vectors {\tt x} are
interleaved so that {\tt x}$^l_i$ and {\tt x}$^{l+1}_i$ are
consecutive in memory. The vector {\tt y} is similarly interleaved,
grouped in sets of 16, which correspond to four derivatives applied to
four functions, at a single point.
